Enter our title here

### 2017-08-15 manuscript.tex
draft of course exercise structure

\section{Introduction}

@@

\subsection{Creating a DataCamp Course}
To create a course on DataCamp you will first need to create a DataCamp account by visiting website\www.datacamp.com/teach and
have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are 
make through DataCamp will update the GitHub repository and visa versa. The GitHub repository will contain three files: 
README.md, course.yml, and chapter1.Rmd.
Readme.md contains helpful information of how to get started, citing resourses to learn more about the process. 
course.yml is a file that contains general information about the course you're creating: title, university, description, 
difficulty level, ect.  
chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
ect.

@@

>>>>

\section{Introduction}
\usepackage{hyperref}

@@

\subsection{Creating a DataCamp Course}
To create a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are 
make through DataCamp will update the GitHub repository and visa versa. The GitHub repository will contain three files: 
README.md, course.yml, and chapter1.Rmd.
Readme.md contains helpful information of how to get started, citing resourses to learn more about the process. 
course.yml is a file that contains general information about the course you're creating: title, university, description, 
difficulty level, ect.  
chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
ect.

Educators are able to edit their courses in a number of ways but the 'Teach Editor' located in the teach dashboard is the
most straight forward editor. The 'Teach Editor' is specifically designed to make the creation process of a DataCamp course
as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
also be done through GitHub's online editor and through git locally but these methods do not allow for automatic content
previewing.

@@

A 'NormalExercise' is an interactive coding exercise containing a lesson section, instructions, pre-exercise code, sample 
code, hint, solution and a submission correctness testing coded (SCT). However, the interface for students (or the 'Preview
mode) only includes the lesson, Instructions, R script panel and a R console panel.

In the 'assignment' portion of the exercise, instructors can add additional information about the assignment that will help
students understand and complete the instructions. The Instructions section will contain the actual task the student is 
asked to execute. The 'pre-exercise code' sets up the workspace for the student; this section will contain code to import
data sets, install packages and any other operation that you want to be in the workspace but hidden from students. The 'sample
code' section contains code or notes that students view in the R script panel. Students' also use the R script panel to write
the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
on the 'Hint' button or eventually the 'solution'.

Solution Correctness Test code..
